\morus: Biases in the Stream

### 2018-05-10 morusAC_05_Full_trails.tex
minor update

\subsection{Symmetrizing the Trail}
In order to build a trail on the full \cipher{MORUS}, we proceed exactly like we did for \cipher{MiniMORUS}, following the exact same path down to step and word rotation values, with one difference: in order to move from the one-word registers of \cipher{MiniMORUS} to the four-word registers of full \cipher{MORUS}, we make every term $S^t_{i,j}$ and $C^t_j$ symmetric, in the sense of \Cref{sec/introminimorus}.
That is, for every $S^t_{i,j}$ (resp. $C^t_j$) component in every trail fragment and every equation, we \emph{symmetrize} the term by adding in the terms $S^t_{i,j+w}$, $S^t_{i,j+2w}$, $S^t_{i,j+3w}$ (resp. $C^t_{j+w}$, $C^t_{j+2w}$, $C^t_{j+3w}$), where as usual $w$ denotes the word size. For example, if $w=64$ (for \cipher{MORUS1280}), the term $S^3_{2,0}$ is symmetrized into:
\[
S^3_{2,0} \oplus S^3_{2,64} \oplus S^3_{2,128} \oplus S^3_{2,192}.
\]

>>>>

\subsection{Symmetrizing the Trail}
In order to build a trail on the full \cipher{MORUS}, we proceed exactly like we did for \cipher{MiniMORUS}, following exactly the same path down to step and word rotation values, with one difference: in order to move from the one-word registers of \cipher{MiniMORUS} to the four-word registers of full \cipher{MORUS}, we make every term $S^t_{i,j}$ and $C^t_j$ symmetric, in the sense of \Cref{sec/introminimorus}.
That is, for every $S^t_{i,j}$ (resp. $C^t_j$) component in every trail fragment and every equation, we \emph{symmetrize} the term by adding in the terms $S^t_{i,j+w}$, $S^t_{i,j+2w}$, $S^t_{i,j+3w}$ (resp. $C^t_{j+w}$, $C^t_{j+2w}$, $C^t_{j+3w}$), where as usual $w$ denotes the word size. For example, if $w=64$ (for \cipher{MORUS1280}), the term $S^3_{2,0}$ is symmetrized into:
\[
S^3_{2,0} \oplus S^3_{2,64} \oplus S^3_{2,128} \oplus S^3_{2,192}.
\]
